Chinese Character Style Transfer with conditional GAN

### 2018-05-02 report/final/egpaper_final.tex
clean up

\subsection{Font Style Transfer}
A number of previous works have also studied the character style transfer process. "From A to Z" perform style transfer on English characters using variational autoencoder (VAE) \cite{DBLP:journals/corr/UpchurchSB16}. A online project zi2zi borrows idea from pix2pix, using GAN with encoder-decoder and the U-net structure in the generator to perform font generation in a latent space created by some fixed font styles. Another work AEGN also uses GAN to generate calligraphy using a standard font directly \cite{DBLP:journals/corr/LyuBYZHL17}. A more recent and aligned work is the EMD model, which separate the content and style representation using two distinct encoders \cite{DBLP:journals/corr/abs-1711-06454}.

>>>>

\subsection{Font Style Transfer}
A number of previous works have also studied the character style transfer process. "From A to Z" perform style transfer on English characters using variational autoencoder (VAE) \cite{DBLP:journals/corr/UpchurchSB16}. A online project zi2zi\cite{zi2zi} borrows idea from pix2pix, using GAN with encoder-decoder and the U-net structure in the generator to perform font generation in a latent space created by some fixed font styles. Another work AEGN also uses GAN to generate calligraphy using a standard font directly \cite{DBLP:journals/corr/LyuBYZHL17}. A more recent and aligned work is the EMD model, which separate the content and style representation using two distinct encoders \cite{DBLP:journals/corr/abs-1711-06454}.
